---
title: "Overview report"
output: pdf_document
params:
  time_data: NA
  la: NA
  kpo_data: NA
  comms_data: NA
  info_data: NA
  staff_data: NA
  resp_data: NA
  fair_data: NA
  overall_data: NA
---

```{r echo = F}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r echo = F}
# The `params` object is available in the document.
kpo_data <- params$kpo_data
time_data <- params$time_data
comms_data <- params$comms_data
info_data <- params$info_data
staff_data <- params$staff_data
resp_data <- params$resp_data
fair_data <- params$fair_data
overall_data <- params$overall_data
la <- params$la
```


# Individual Questions

## Time taken
```{r echo=FALSE, comment= ""}
##Set up for time taken graph and text
#load data and split into Scotland and LA datasets
     text_prep <- function(dataset){
     qstnDta <- dataset
     qstnDta_LA <- qstnDta %>% filter(Selection == "LA")
     qstnDta_scot<- qstnDta %>% filter(Selection == "Scotland")
     #get total percentage good or very good 
     total_good <- filter(qstnDta_LA, value %in% c(1,2) & Selection == "LA") %>% pull(perc_resp) %>%
       sum()
     #if this is above 55% then overall is positive, otherwise negative/balances
     pos_or_neg <- ifelse(total_good > 0.55, "mainly positive", ifelse(total_good < 0.45, "mainly negative", "balanced"))
     
     #get the name for the maximum value in LA dataset. If more than one paste these together
     max_name <- as.character(qstnDta_LA %>% filter(n == max(n)) %>% pull(named_value))
     if(length(max_name >1)){
       max_name <- paste(max_name, collapse = " & ")
     }
     #Get the pecentage for the highest response and paste together if multiple
     max_perc <- qstnDta_LA %>% filter(n == max(n)) %>% pull(perc_resp)
     if(length(max_perc) >1){
       max_perc <- paste(paste(max_perc, collapse = " & "), "percent respectively.")
     } else{
       max_perc <- paste0(max_perc, "percent.")
     }
     
     #Gte second highest value
     sec_val <- sort(qstnDta_LA$n, partial= 3)[3]
     #Filter for second highest value's name
     sec_name <- qstnDta_LA %>% filter(n == sec_val) %>% pull(named_value)
     if(length(sec_name) >1){
       sec_name <- paste(sec_name, collapse = " & ")
     }
     
     #Filter for second highest value's value
     sec_perc <- qstnDta_LA %>% filter(n == sec_val) %>% pull(perc_resp)
     if(length(sec_perc) >1){
       sec_perc <- paste(paste(sec_perc, collapse = " & "), "percent respectively.")
     }else{
       sec_perc <- paste0(sec_perc, " percent.")
     }
     
     #get most frequent response for Scotland
     scot_max_name <- as.character(qstnDta_scot %>% filter(n == max(n)) %>% pull(named_value))
     
     if(length(scot_max_name) >1){
       scot_max_name <- paste(scot_max_name, collapse = " & ")
     }
     #get percentage for most frequent Scotland level response
     scot_max_perc <- qstnDta_scot %>% filter(n == max(n)) %>% pull(perc_resp)
     if(length(scot_max_perc) >1){
       scot_max_perc <- paste(paste(scot_max_perc, collapse = " & "), "percent respectively.")
     } else{
       scot_max_perc <- paste0(scot_max_perc, "percent.")
     }
     #assign all objects as specifically for this question dataset
     objcts <- list(
     pos_or_neg,
     total_good,
     max_name,
     max_perc,
     sec_name,
     sec_perc,
     sec_name,
     sec_perc,
     scot_max_name,
     scot_max_perc)
     
     names(objcts) <- c("pos_or_neg","total_good","max_name", "max_perc","sec_name","sec_perc",
     "sec_name","sec_perc", "scot_max_name", "scot_max_perc")
     return(objcts)
     }

tm <- text_prep(time_data)
```
In this year for `r la` to date for the question "Thinking of your engagement, how satisfied were you with the time taken to complete the process?"" responses have been `r tm$pos_or_neg` with `r tm$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r tm$max_name` at `r tm$max_perc` This was followed by `r tm$sec_name` at `r tm$sec_perc` For Scotland overall, most respondents said that they were `r tm$scot_max_name` at `r tm$scot_max_perc`


```{r echo = F}
     ggplot(data = time_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```
## Communications
```{r echo=FALSE, comment= ""}
cm_txt <- text_prep(comms_data)
```
In this year for `r la` to date for the question "How would you rate the standard of communication provided?" responses have been `r cm_txt$pos_or_neg` with `r cm_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r cm_txt$max_name` at `r cm_txt$max_perc` This was followed by `r cm_txt$sec_name` at `r cm_txt$sec_perc` For Scotland overall, most respondents said that they were `r cm_txt$scot_max_name` at `r cm_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = comms_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```

## Information
```{r echo=FALSE, comment= ""}
inf_txt <- text_prep(info_data)
```
In this year for `r la` to date for the question "How would you rate the quality of information provided?" responses have been `r inf_txt$pos_or_neg` with `r inf_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r inf_txt$max_name` at `r inf_txt$max_perc` This was followed by `r inf_txt$sec_name` at `r inf_txt$sec_perc` For Scotland overall, most respondents said that they were `r inf_txt$scot_max_name` at `r inf_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = info_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```

## Staff
```{r echo=FALSE, comment= ""}
staff_txt <- text_prep(staff_data)
```
In this year for `r la` to date for the question "How would you rate the service offered by staff?" responses have been `r inf_txt$pos_or_neg` with `r inf_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r inf_txt$max_name` at `r inf_txt$max_perc` This was followed by `r inf_txt$sec_name` at `r inf_txt$sec_perc` For Scotland overall, most respondents said that they were `r inf_txt$scot_max_name` at `r inf_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = staff_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```

## Responsiveness
```{r echo=FALSE, comment= ""}
resp_txt <- text_prep(resp_data)
```
In this year for `r la` to date for the question "How would you rate responsiveness to any queries or issues raised?" responses have been `r resp_txt$pos_or_neg` with `r resp_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r resp_txt$max_name` at `r resp_txt$max_perc` This was followed by `r resp_txt$sec_name` at `r resp_txt$sec_perc` For Scotland overall, most respondents said that they were `r resp_txt$scot_max_name` at `r resp_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = resp_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```

## Treated Fairly
```{r echo=FALSE, comment= ""}
fair_txt <- text_prep(fair_data)
```
In this year for `r la` to date for the question "How would you rate responsiveness to any queries or issues raised?" responses have been `r fair_txt$pos_or_neg` with `r fair_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r fair_txt$max_name` at `r fair_txt$max_perc` This was followed by `r fair_txt$sec_name` at `r fair_txt$sec_perc` For Scotland overall, most respondents said that they were `r fair_txt$scot_max_name` at `r fair_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = fair_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```

## Overall Satisfaction
```{r echo=FALSE, comment= ""}
ovr_txt <- text_prep(overall_data)
```
In this year for `r la` to date for the question "Overall, how satisfied were you with the service provided?" responses have been `r ovr_txt$pos_or_neg` with `r ovr_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r ovr_txt$max_name` at `r ovr_txt$max_perc` This was followed by `r ovr_txt$sec_name` at `r ovr_txt$sec_perc` For Scotland overall, most respondents said that they were `r ovr_txt$scot_max_name` at `r ovr_txt$scot_max_perc`

```{r echo = F}
     ggplot(data = overall_data ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
```