---
title: "Dynamic report"
output: pdf_document
params:
  n: NA
---

```{r echo = F}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r echo = F}
# The `params` object is available in the document.
dta <- params$n
```

```{r echo=FALSE, comment= ""}
#load data and split into Scotland and LA datasets
     qstnDta <- dta
     qstnDta_LA <- qstnDta %>% filter(Selection == "LA")
     qstnDta_scot<- qstnDta %>% filter(Selection == "Scotland")
     #get total percentage good or very good 
     total_good <- filter(qstnDta_LA, value %in% c(1,2) & Selection == "LA") %>% pull(perc_resp) %>%
       sum()
     #if this is above 55% then overall is positive, otherwise negative/balances
     pos_or_neg <- ifelse(total_good > 0.55, "mainly positive.", ifelse(total_good < 0.45, "mainly negative.", "balanced."))
     
     #get the name for the maximum value in LA dataset. If more than one paste these together
     max_name <- as.character(qstnDta_LA %>% filter(n == max(n)) %>% pull(named_value))
     if(length(max_name >1)){
       max_name <- paste(max_name, collapse = " & ")
     }
     #Get the pecentage for the highest response and paste together if multiple
     max_perc <- qstnDta_LA %>% filter(n == max(n)) %>% pull(perc_resp)
     if(length(max_perc) >1){
       max_perc <- paste(paste(max_perc, collapse = " & "), "percent respectively.")
     } else{
       max_perc <- paste0(max_perc, "percent.")
     }
     
     #Gte second highest value
     sec_val <- sort(qstnDta_LA$n, partial= 3)[3]
     #Filter for second highest value's name
     sec_name <- qstnDta_LA %>% filter(n == sec_val) %>% pull(named_value)
     if(length(sec_name) >1){
       sec_name <- paste(sec_name, collapse = " & ")
     }
     
     #Filter for second highest value's value
     sec_perc <- qstnDta_LA %>% filter(n == sec_val) %>% pull(perc_resp)
     if(length(sec_perc) >1){
       sec_perc <- paste(paste(sec_perc, collapse = " & "), "percent respectively.")
     }else{
       sec_perc <- paste0(sec_perc, " percent.")
     }
     
     #get most frequent response for Scotland
     scot_max_name <- as.character(qstnDta_scot %>% filter(n == max(n)) %>% pull(named_value))
     
     if(length(scot_max_name) >1){
       scot_max_name <- paste(scot_max_name, collapse = " & ")
     }
     #get percentage for most frequent Scotland level response
     scot_max_perc <- qstnDta_scot %>% filter(n == max(n)) %>% pull(perc_resp)
     if(length(scot_max_perc) >1){
       scot_max_perc <- paste(paste(scot_max_perc, collapse = " & "), "percent respectively.")
     } else{
       scot_max_perc <- paste0(scot_max_perc, "percent.")
     }
```

###Time takens
In this year to date for the question "Thinking of your engagement, how satisfied were you with the time taken to complete the process?"" responses have been `r pos_or_neg` with `r total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r max_name` at `r max_perc` This was followed by `r sec_name` at `r sec_perc` For Scotland overall, most respondents said that they were `r scot_max_name` at `r scot_max_perc`

A plot of `params$n` random points.

```{r echo = F}
     ggplot(data = dta ) +
       geom_bar(aes(x = reorder(named_value, as.numeric(value)), y = perc_resp, fill =Selection), stat= "identity", position = "dodge")
     ```