---
title: "National Customer Survey Performance Overview Report"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
fontsize: 11pt
params:
  time_data: NA
  la: NA
  year: NA
  quarter: NA
  named_qrtr: NA
  type_data: NA
  reason_data: NA
  respondent_data: NA
  kpo_data: NA
  line_data: NA
  comms_data: NA
  info_data: NA
  staff_data: NA
  responsive_data: NA
  fair_data: NA
  overall_data: NA
---

```{r echo = FALSE}
library(knitr)
opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

```{r echo = FALSE}
# The `params` object is available in the document.
kpo_data <- params$kpo_data
type_data <- params$type_data
reason_data <- params$reason_data
respondent_data <- params$respondent_data
line_data <- params$line_data
time_data <- params$time_data
comms_data <- params$comms_data
info_data <- params$info_data
staff_data <- params$staff_data
responsive_data <- params$responsive_data
fair_data <- params$fair_data
overall_data <- params$overall_data
la <- params$la
year <- params$year
quarter <- params$quarter
named_qrtr <- params$named_qrtr
```

## KPO 4 Score
```{r echo = FALSE, comment = ""}
# Set up text for KPO4 

# Store the number of financial years available for council
all_kpo_data <- kpo_data
Years <- all_kpo_data %>% filter(id == la)
Years <- length(unique(Years$`Financial Year`))

# Filter the data depending on number of years
# If only one use year available, otherwise use current financial year
kpo_data1 <- if (Years > 1) {
  kpo_data %>% 
  filter(`Tracking Link` == "Total" & `Financial Year` == crnt_fin_yr)
} else {
  kpo_data %>% 
    filter(`Tracking Link` == "Total" & `Financial Year` == year)
}

# Council KPO4
KPO4_ytd <- kpo_data1 %>% filter(id == la) %>% pull(KPO_score)
# Scotland KPO4
scotAv_kpo4 <- kpo_data1 %>% filter(id == "Scotland") %>% pull(KPO_score)

# Compare council KPO4 values with Scotland and target to create 
# reactive text values
hilow_kpo4 <- ifelse(KPO4_ytd > 7.5, 
                     "higher than", 
                     ifelse(KPO4_ytd < 7.5, "lower than", "equal to")
                     )
abbel_kpo4 <- ifelse(KPO4_ytd > scotAv_kpo4, 
                     "higher than", 
                     ifelse(KPO4_ytd < scotAv_kpo4, 
                            "lower than", 
                            "equal to"
                            )
                     )

# Store value for previous financial year
KPO4_prev <- all_kpo_data %>% 
  filter(`Tracking Link` == "Total" & `Financial Year` == prev_fin_yr)
KPO4_prev <- KPO4_prev %>% filter(id == la) %>% pull(KPO_score)
# Create text for comparison with previous year
change_value <- KPO4_ytd - KPO4_prev
change_text <- if_else(change_value < 0, "a decrease", "an increase")
     
# Text for when there is only 1 financial year
text_kpo <- paste0("This indicator summarises performance across all questions, with differential weightings based on importance. For ",
la,
" in ",
year, 
" overall performance is at ", 
KPO4_ytd, 
" for the year to date. This is ",
abbel_kpo4,
" the Scotland average of ", 
scotAv_kpo4,
" and ", 
hilow_kpo4,
" the target value of 7.5."
)
     
# Text for when there are more than 1 financial years     
text_multiple_kpo <- paste0("This indicator summarises performance across all questions, with differential weightings based on importance. For ", 
la,
" in ",
crnt_fin_yr, 
" overall performance is at ", 
KPO4_ytd, 
" for the year to date. This reflects ", 
change_text,
" of ", 
change_value, 
" points from the performance of ", 
KPO4_prev, 
" in ", 
prev_fin_yr, 
". The year to date performance of ", 
la, 
" in ", 
crnt_fin_yr, 
" is ", 
abbel_kpo4,
" the Scotland average of ", 
scotAv_kpo4,
" and ", 
hilow_kpo4,
" the target value of 7.5."
)
```

`r ifelse(Years > 1, text_multiple_kpo, text_kpo)`


```{r echo = FALSE}
# Create graph for KPO4 YTD
     
kpo_data1 <- kpo_data %>% filter(`Tracking Link` == "Total")
# Set the council values as a factor so the data can be arranged to have the council first regardless of alphabetical order
kpo_data1$id <- factor(kpo_data1$id, levels = c(la, "Scotland"))
kpo_data1 <- arrange(kpo_data1, id)
     
# Store number of years to determine the number of reps for colours of bars
Years <- length(unique(kpo_data1$`Financial Year`))

ggplot(data = kpo_data1,
       aes(x = `Financial Year`, 
           y = KPO_score, 
           fill = id
           )
       ) +
  geom_bar(stat = "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black") +
  geom_text(aes(label = KPO_score, y = KPO_score + 0.8), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_y_continuous(limits = c(0, 11), 
                     expand = expansion(mult = c(0, 0.1))
                     ) +
  scale_fill_manual(values = rep(c("cadetblue3", "dimgrey"), Years),
                    name = ""
                    ) +
  ggtitle("KPO 4 score - Year to Date") +
  xlab("") +
  ylab("KPO 4 Score") +
  theme_classic()
```
\newpage

# Respondent Type
```{r echo = FALSE, comment = ""}
# Set up text for respondent type
type_dta_filter <- respondent_data %>% filter(question_type == "Type") 
# Get total responses for referencing the percentage denominator
type_number <- type_dta_filter %>% 
  group_by(Question) %>%
  summarise_at(vars(`n`),sum)
type_number <- type_number[1, 2]
# Create variables for percentages for different groups
agent_perc <- type_dta_filter[type_dta_filter$Question == "Agent/Designer" & type_dta_filter$value == 1 ,"perc"] %>% 
  pull(perc)

appli_perc <- type_dta_filter[type_dta_filter$Question == "Applicant" & type_dta_filter$value == 1 ,"perc"] %>% 
  pull(perc)

contr_perc <- type_dta_filter[type_dta_filter$Question == "Contractor" & type_dta_filter$value == 1 ,"perc"] %>% 
  pull(perc)

type_other_perc <- type_dta_filter[type_dta_filter$Question == "Other" & type_dta_filter$value == 1 ,"perc"] %>% 
  pull(perc)

# If any are 0 then replace with "none"
agent_perc <- ifelse(isEmpty(agent_perc), "none", paste0(agent_perc, "%"))
appli_perc <- ifelse(isEmpty(appli_perc), "none", paste0(appli_perc, "%"))
contr_perc <- ifelse(isEmpty(contr_perc), "none", paste0(contr_perc, "%"))
type_other_perc <- ifelse(isEmpty(type_other_perc), 
                          "No respondents", 
                          paste0(type_other_perc, "%"))
```

  
Respondents were asked to provide details on the type of respondent they were, as well as their reason for contacting the Building Standards Service in `r la`. Of the `r type_number` respondents in `r named_qrtr` `r year`, `r agent_perc` were agents or designers, `r appli_perc` were applicants and `r contr_perc` were contractors. `r type_other_perc` said they were an other respondent type.  



```{r echo = FALSE}
ggplot(data = type_data, aes(x = Question, y = perc)) +
  geom_col(fill = "cadetblue3", colour = "black") +
  geom_text(aes(label = perc, y = perc + 2.5), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +

  ggtitle(paste("Respondent Type: \n", named_qrtr, year)) +

  xlab("Respondent Type") +
  ylab("Percentage of Responses")
```
\newpage

# Response Reason
```{r echo= FALSE, comment = ""}
# Set up text for response reason
resp_dta_filter <- respondent_data %>% filter(question_type == "Reason") 
# Get total responses for referencing the percentage denominator
resp_number <- resp_dta_filter %>% 
  group_by(Question) %>%
  summarise_at(vars(`n`), sum)
resp_number <- resp_number[1, 2]
# Calculate percentages for each response type
discuss_perc <- resp_dta_filter[resp_dta_filter$Question == "To discuss your proposal before applying for a building warrant" & 
                                  resp_dta_filter$value == 1, "perc"] %>% 
  pull(perc)

appli_perc <- resp_dta_filter[resp_dta_filter$Question == "To make an application for a building warrant" & 
                                resp_dta_filter$value == 1 ,"perc"] %>%
  pull(perc)

constr_perc <- resp_dta_filter[resp_dta_filter$Question == "During construction, including submission of a completion certificate" &
                                 resp_dta_filter$value == 1 ,"perc"] %>% 
  pull(perc)

other_perc <- resp_dta_filter[resp_dta_filter$Question == "Other" &
                                resp_dta_filter$value == 1 ,"perc"] %>%
  pull(perc)
     
# If any are 0 then replace with "none"
discuss_perc <- ifelse(isEmpty(discuss_perc), 
                       "none", 
                       paste0(discuss_perc,"%")
                       )
appli_perc <- ifelse(isEmpty(appli_perc), "none", paste0(appli_perc, "%"))
constr_perc <- ifelse(isEmpty(constr_perc), "none", paste0(constr_perc, "%"))
other_perc <- ifelse(isEmpty(other_perc), 
                     "No respondents", 
                     paste0(other_perc, "%")
                     )
```

  
Respondents were asked to provide details on the type of respondent they were, as well as their reason for contacting the Building Standards Service in `r la`. Of the `r resp_number` respondents in, `r named_qrtr` `r year`, `r discuss_perc` contacted the local authority to discuss their proposal before applying for a building warrant, `r appli_perc` were making an application for a warrant and `r constr_perc` contacted the service during construction. `r other_perc` contacted the service for some other reason.  


```{r echo = FALSE}
ggplot(data = reason_data,aes(x = Question, y = perc)) +
  geom_col(fill = "cadetblue3", colour = "black") +
  geom_text(aes(label = perc, y = perc + 2.5), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Response Reason: \n", named_qrtr, year)) +

  xlab("Reason") +
  ylab("Percentage of Responses")
```
\newpage

# KPO 4 Over Time
```{r echo = FALSE, comment = ""}
# Store the number of financial years available for council
Years <- kpo_data %>% filter(id == la)
Years <- length(unique(Years$`Financial Year`))
Years <- if_else(Years > 1, crnt_fin_yr, year)

# Filter to quarters, selected council and current financial year
kpo_data1 <- kpo_data %>% 
  filter(`Tracking Link` != "Total",
         `Financial Year` == Years,  
         id == la
         ) %>% 
  ungroup()
     
# Set the quarter labels as a factor to ensure they stay in order
QLabels <- unique(kpo_data1$`Tracking Link`)
kpo_data1$`Tracking Link` <- factor(kpo_data1$`Tracking Link`, 
                                    levels = QLabels
                                    )
     
# Store the names of the quarters by position (can't just reference by quarter number as some councils may have data missing).
# If there is a quarter missing the position will be empty
first_Q <- kpo_data1$`Tracking Link`[[1]]
second_Q <- if (length(QLabels) > 1) {
  kpo_data1$`Tracking Link`[[2]]
} else {
    0
  }
third_Q <- if (length(QLabels) > 2) {
  kpo_data1$`Tracking Link`[[3]]
} else {
    0
  }
fourth_Q <- if (length(QLabels) > 3) {
  kpo_data1$`Tracking Link`[[4]]
} else {
    0
  }
    
# Filter to get KPO for first quarter available
Q1_kpo <- kpo_data1 %>% 
  filter(`Tracking Link` == first_Q) %>%
  select(KPO_score)
# Render text for quarter 1
Q1_text <- paste0("In ", 
                  first_Q,
                  " ",
                  Years,
                  " performance for KPO 4 calculated across all responses for all questions was ",
                  Q1_kpo,
                  " for ", 
                  la,
                  ". "
                  )
# Filter to get KPO for second quarter available
Q2_kpo <- kpo_data1 %>% 
  filter(`Tracking Link` == second_Q) %>%
  select(KPO_score)
# Compare quarter 2 and quarter 1
comp_Q12 <- tryCatch({
  ifelse(Q2_kpo > Q1_kpo + 0.2, 
         "rose", 
         ifelse(Q2_kpo < Q1_kpo - 0.2, "fell", "stayed the same")
         )
  },
  error = function(error_message) {""}
  )
# Render text for when there are 2 quarters                 
Q2_text <- paste0(Q1_text,
                  "Performance then ", 
                  comp_Q12,
                  " in ", 
                  second_Q, 
                  " to stand at ", 
                  Q2_kpo, 
                  "."
                  )
# Filter to get KPO for third quarter available
Q3_kpo <- kpo_data1 %>% 
  filter(`Tracking Link` == third_Q) %>%
  select(KPO_score)
# Compare third & second quarter available - ignore if error occurs
comp_Q23 <- tryCatch({
  ifelse(Q3_kpo > Q2_kpo + 0.2, 
         "higher than", 
         ifelse(Q3_kpo < Q2_kpo - 0.2, "lower than", "the same as")
         )
  }, 
  error = function(error_message) {""}
  )
# Render text for when there are 3 quarters                    
Q3_text <- paste0(Q2_text,
                  " In ", 
                  third_Q, 
                  " performance was ", 
                  comp_Q23,
                  " ", 
                  second_Q,
                  " at ", 
                  Q3_kpo,
                  "."
                  )
# Filter to get KPO for fourth quarter available  
Q4_kpo <- kpo_data1 %>% 
  filter(`Tracking Link` == fourth_Q) %>%
  select(KPO_score)
# Compare fourth and third quarter available - ignore if error occurs
comp_Q34 <- tryCatch({
  ifelse(Q4_kpo > Q3_kpo + 0.2, 
         "higher than", 
         ifelse(Q4_kpo < Q3_kpo - 0.2, "lower than", "the same as")
         )
  },
  error = function(error_message) {""}
  )
# Render text for when there are four quarters                    
Q4_text<- paste0(Q3_text, 
                 " In ", 
                 fourth_Q,
                 " performance was ", 
                 comp_Q34,
                 " ",
                 third_Q,
                 " and stands at ",
                 Q4_kpo, 
                 "."
                 )

# Select what text to include based on the no. of quarters available     
main_text <- ifelse(length(QLabels) == 1, 
                    Q1_text, 
                    ifelse(length(QLabels) == 2, 
                           Q2_text, 
                           ifelse(length(QLabels) == 3, 
                                  Q3_text, 
                                  Q4_text
                                  )
                           )
                    )
# If there is data for more than 1 financial year compare most recent quarter with same quarter in previous year
extra_data <- kpo_data
# Filter to current quarter and selected council
extra_data <- extra_data %>% 
  filter(`Tracking Link` == crnt_qtr, id == la)
# Store values for current financial year and previous financial year
first_fin_yr <- if (length(extra_data$`Tracking Link`) > 1) {
  filter(extra_data, `Financial Year` == prev_fin_yr) %>%
    ungroup() %>%
    select(KPO_score)
  } else {
    0
    }
second_fin_yr <- if (length(extra_data$`Tracking Link`) > 1) {
  filter(extra_data, `Financial Year` == Years) %>%
    ungroup() %>%
    select(KPO_score)
} else {
    0
  }
# Compare values and create text
extra_comp <- tryCatch({
  ifelse(second_fin_yr > first_fin_yr + 0.2, 
         " higher than in ", 
         ifelse(second_fin_yr < first_fin_yr - 0.2, 
                " lower than in ",
                " the same as in "
                )
         )
  }, error = function(error_message) {""}
  )
extra_comp_value <- ifelse(extra_comp == " the same as in ",
                           "", 
                           second_fin_yr - first_fin_yr
                           )
extra_text <- paste0("KPO 4 performance in ", 
                     crnt_qtr, 
                     " ", 
                     Years, 
                     " was ", 
                     extra_comp_value, 
                     extra_comp,
                     crnt_qtr, 
                     " ",
                     prev_fin_yr,
                     "."
                     )
# Number of years
no_years <- length(unique(extra_data$`Financial Year`))
# Select which text is shown based on the no. of years available
```    
    
`r ifelse(no_years > 1, paste(main_text, extra_text), main_text)`
    
```{r echo = FALSE}
# Set the council values as a factor so the data can be arranged to have the council first regardless of alphabetical order
line_data$LA <- factor(line_data$LA, levels = c(la, "Scotland"))

# Add Financial year to quarter labels
line_data$`Tracking Link` <- gsub("Quarter\\ ",
                                  "Q",
                                  line_data$`Tracking Link`, 
                                  perl = TRUE
                                  )
line_data$Label <- paste(line_data$`Tracking Link`, 
                         line_data$`Financial Year`, 
                         sep = " "
                         )
line_data$`Tracking Link` <- gsub("Q",
                                  "",
                                  line_data$`Tracking Link`, 
                                  perl = TRUE
                                  )

# Arrange the data to set the order of colours
line_data <- arrange(line_data, `Financial Year`, `Tracking Link`, LA)
      
# Set the date labels as a factor to ensure they stay in order
QLabels <- unique(line_data$Label)
line_data$Label <- factor(line_data$Label, levels = QLabels)
```
  
  
```{r, eval = length(line_data$LA[line_data$LA == la]) > 1, echo = FALSE}
# The above test whether there is more than one data point available for the council and will only evaluate the code below if this is TRUE
ggplot(data = line_data,
       aes(x = Label, y = KPO_score, group = LA, colour = LA)
       ) +
  geom_line(lwd = 1) +
  geom_text(aes(label = KPO_score, y = KPO_score + 0.1), 
            vjust = 0,
            position = position_dodge(width = 0),
            show.legend = FALSE
            ) +
  # Span x axis labels over multiple lines
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
  scale_color_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  ggtitle("KPO 4 score - over time") +
  xlab("") +
  ylab("KPO 4 Score") +
  theme_classic()
```
  
  
```{r, eval = length(line_data$LA[line_data$LA == la]) < 2, echo = F}
# The above test whether there is only one data point available for the council and will only evaluate the code below if this is TRUE

# Pulls out quarter and financial year available for selected council
# There may be more than one quarter for Scotland so need to filter so that's not included
qrtr_available <- line_data$`Tracking Link`[line_data$LA == la]
year_available <- line_data$`Financial Year`[line_data$LA == la]
      
line_data <- line_data %>% 
  filter(`Tracking Link` == qrtr_available, 
         `Financial Year` == year_available
         )

ggplot(data = line_data,
       aes(x = `Tracking Link`, 
           y = KPO_score, 
           fill = LA
           )
       ) +
  geom_bar(stat = "identity",
           position = "dodge",
           width = 0.7, 
           colour = "black"
           ) +
  geom_text(aes(label = KPO_score, y = KPO_score + 0.8), 
            vjust = 0,
            position = position_dodge(width = 0.9)
            ) +
  scale_y_continuous(limits = c(0,11), 
                     expand = expansion(mult = c(0, 0.1))
                     ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  ggtitle("KPO 4 score - over time") +
  xlab("") +
  ylab("KPO 4 Score") +
  theme_classic()
```
\newpage

# Individual Questions

## Time taken
```{r echo = FALSE, comment= ""}
# Create function for preparing text values for individual questions
text_prep <- function(dataset) {
  # Load data and split into Scotland and LA datasets
  qstnDta <- dataset
  qstnDta_LA <- qstnDta %>% filter(Selection == la)
  qstnDta_scot <- qstnDta %>% filter(Selection == "Scotland")
  # Get total percentage positive
  total_good <- filter(qstnDta_LA, value %in% c(1,2) & Selection == la) %>%
    pull(perc_resp) %>%
    sum()
  # If this is above 55% then overall is positive, If less than 45% negative,   otherwise balanced
  pos_or_neg <- ifelse(total_good > 55, 
                       "mainly positive", 
                       ifelse(total_good < 45, 
                              "mainly negative", 
                              "balanced"
                              )
                       )
  # Add "only" to the % positive if this is below 45
  if (total_good < 45) {
    total_good <- paste("only", total_good)
  } else {
    total_good <- total_good
    }
  
  # Get the name for the maximum value in LA dataset. 
  # If more than one paste these together
  max_name <- as.character(qstnDta_LA %>% 
                             filter(n == max(n)) %>%
                             pull(named_value)
                           )
  if (length(max_name > 1)) {
    max_name <- paste(max_name, collapse = " & ")
  }
  # Get the percentage for the highest response and paste together if 
  # multiple
  max_perc <- qstnDta_LA %>% 
    filter(n == max(n)) %>% 
    pull(perc_resp)
  if (length(max_perc) > 1) {
    max_perc <- paste(paste(max_perc, collapse = " & "), 
                      "percent respectively."
                      )
    } else {
      max_perc <- paste0(max_perc, " percent.")
      }
  # Get second highest value
  sec_val <- sort(qstnDta_LA$n, partial = 3)[3]
  # Filter for second highest value's name
  sec_name <- qstnDta_LA %>% 
    filter(n == sec_val) %>% 
    pull(named_value)
  if (length(sec_name) > 1) {
    sec_name <- paste(sec_name, collapse = " & ")
    }
  # Filter for second highest value's value
  sec_perc <- qstnDta_LA %>% 
    filter(n == sec_val) %>% 
    pull(perc_resp)
  if (length(sec_perc) > 1) {
    sec_perc <- paste(paste(sec_perc, collapse = " & "), 
                      "percent respectively."
                      )
    } else {
      sec_perc <- paste0(sec_perc, " percent.")
      }
  
  # Get most frequent response for Scotland
  scot_max_name <- as.character(qstnDta_scot %>% 
                                  filter(n == max(n)) %>% 
                                  pull(named_value)
                                )
  if (length(scot_max_name) > 1) {
    scot_max_name <- paste(scot_max_name, collapse = " & ")
    }
  # Get percentage for most frequent Scotland level response
  scot_max_perc <- qstnDta_scot %>% 
    filter(n == max(n)) %>% 
    pull(perc_resp)
  if (length(scot_max_perc) > 1) {
    scot_max_perc <- paste(paste(scot_max_perc, collapse = " & "), 
                           "percent respectively."
                           )
    } else {
      scot_max_perc <- paste0(scot_max_perc, " percent.")
      }
  
  # Assign all objects so they can be referenced in the question dataset
  objcts <- list(pos_or_neg,
                 total_good,
                 max_name,
                 max_perc,
                 sec_name,
                 sec_perc,
                 sec_name,
                 sec_perc,
                 scot_max_name,
                 scot_max_perc
                 )
  names(objcts) <- c("pos_or_neg",
                     "total_good",
                     "max_name", 
                     "max_perc",
                     "sec_name",
                     "sec_perc",
                     "sec_name",
                     "sec_perc", 
                     "scot_max_name", 
                     "scot_max_perc"
                     )
  return(objcts)
  }
# Set up for time taken text
tm <- text_prep(time_data)
```
In `r named_qrtr` `r year`, for the question "Thinking of your engagement, how satisfied were you with the time taken to complete the process?" responses for `r la` have been `r tm$pos_or_neg` with `r tm$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r tm$max_name` at `r tm$max_perc` This was followed by `r tm$sec_name` at `r tm$sec_perc` For Scotland overall, most respondents said that they were `r tm$scot_max_name` at `r tm$scot_max_perc`  


```{r echo = FALSE}
ggplot(data = time_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat = "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9)
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Satisfaction with time taken -", named_qrtr, year)) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +

  theme_classic()
```
\newpage

## Communications
```{r echo = FALSE, comment = ""}
cm_txt <- text_prep(comms_data)
```
In `r named_qrtr` `r year`, for the question "How would you rate the standard of communication provided?" responses for `r la` have been `r cm_txt$pos_or_neg` with `r cm_txt$total_good` percent saying that it was good or very good. The greatest proportion of respondents said they felt it was `r cm_txt$max_name` at `r cm_txt$max_perc` This was followed by `r cm_txt$sec_name` at `r cm_txt$sec_perc` For Scotland overall, most respondents said that communication was `r cm_txt$scot_max_name` at `r cm_txt$scot_max_perc`  


```{r echo = FALSE}
ggplot(data = comms_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0, 
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Standard of Communication -", named_qrtr, year)) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +

  theme_classic()
```
\newpage

## Information
```{r echo = FALSE, comment = ""}
inf_txt <- text_prep(info_data)
```
In `r named_qrtr` `r year`, for the question "How would you rate the quality of information provided?" responses for `r la` have been `r inf_txt$pos_or_neg` with `r inf_txt$total_good` percent saying that it was good or very good. The greatest proportion of respondents said they felt it was `r inf_txt$max_name` at `r inf_txt$max_perc` This was followed by `r inf_txt$sec_name` at `r inf_txt$sec_perc` For Scotland overall, most respondents said that the information they received was `r inf_txt$scot_max_name` at `r inf_txt$scot_max_perc`  

```{r echo = FALSE}
ggplot(data = info_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3","dimgrey"), name = "") +
  ggtitle(paste("Quality of information -", named_qrtr, year)) +
  xlab("Responses") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
```
\newpage

## Staff
```{r echo = FALSE, comment = ""}
staff_txt <- text_prep(staff_data)
```
In `r named_qrtr` `r year`, for the question "How would you rate the service offered by staff?" responses for `r la` have been `r staff_txt$pos_or_neg` with `r staff_txt$total_good` percent saying that it was good or very good. The greatest proportion of respondents said they felt it was `r staff_txt$max_name` at `r staff_txt$max_perc` This was followed by `r staff_txt$sec_name` at `r staff_txt$sec_perc` For Scotland overall, most respondents said that the service received was `r staff_txt$scot_max_name` at `r staff_txt$scot_max_perc`  


```{r echo = FALSE}
ggplot(data = staff_data, 
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Service offered by staff -", named_qrtr, year)) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
```
\newpage

## Responsiveness
```{r echo = FALSE, comment = ""}
resp_txt <- text_prep(responsive_data)
```
In `r named_qrtr` `r year`, for the question "How would you rate the time taken to respond to any queries or issues raised?" responses for `r la` have been `r resp_txt$pos_or_neg` with `r resp_txt$total_good` percent saying that it was good or very good. The greatest proportion of respondents said they were `r resp_txt$max_name` at `r resp_txt$max_perc` This was followed by `r resp_txt$sec_name` at `r resp_txt$sec_perc` For Scotland overall, most respondents said that responsiveness was `r resp_txt$scot_max_name` at `r resp_txt$scot_max_perc`  


```{r echo = FALSE}
ggplot(data = responsive_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  ggtitle(paste("Responsiveness to queries or issues -", named_qrtr, year))+
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
```
\newpage

## Treated Fairly
```{r echo = FALSE, comment = ""}
fair_txt <- text_prep(fair_data)
```
In `r named_qrtr` `r year`, for the question "To what extent would you agree that you were treated fairly?" responses for `r la` have been `r fair_txt$pos_or_neg` with `r fair_txt$total_good` percent saying that they agree or strongly agree. The greatest proportion of respondents said they `r fair_txt$max_name` with the statement at `r fair_txt$max_perc` This was followed by `r fair_txt$sec_name` at `r fair_txt$sec_perc` For Scotland overall, most respondents said that they `r fair_txt$scot_max_name` at `r fair_txt$scot_max_perc`  


```{r echo = FALSE}
ggplot(data = fair_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  ggtitle(paste("Would you agree you were treated fairly -",
                named_qrtr, 
                year)) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
```
\newpage

## Overall Satisfaction
```{r echo = FALSE, comment = ""}
ovr_txt <- text_prep(overall_data)
```
In `r named_qrtr` `r year`, for the question "Overall, how satisfied were you with the service provided?" responses for `r la` have been `r ovr_txt$pos_or_neg` with `r ovr_txt$total_good` percent saying that they were very satisfied or satisfied. The greatest proportion of respondents said they were `r ovr_txt$max_name` at `r ovr_txt$max_perc` This was followed by `r ovr_txt$sec_name` at `r ovr_txt$sec_perc` For Scotland overall, most respondents said that they were `r ovr_txt$scot_max_name` at `r ovr_txt$scot_max_perc`  

```{r echo = FALSE}
ggplot(data = overall_data,
       aes(x = named_value, y = perc_resp, fill = Selection)
       ) +
  geom_bar(stat= "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black"
           ) +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9) 
            ) +
  scale_fill_manual(values = c("cadetblue3", "dimgrey"), name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Overall satisfaction -", named_qrtr, year)) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
```