---
title: "National Customer Survey Performance Overview Report"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{helvet}
  - \usepackage[T1]{fontenc}
  - \renewcommand\familydefault{\sfdefault} 
fontsize: 11pt
params:
  time_data: NA
  la: NA
  year: NA
  quarter: NA
  named_qrtr: NA
  type_data: NA
  reason_data: NA
  respondent_data: NA
  kpo_data: NA
  comms_data: NA
  info_data: NA
  staff_data: NA
  responsive_data: NA
  fair_data: NA
  overall_data: NA
---

```{r echo = FALSE}
library(knitr)
opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

```{r echo = FALSE}
# The `params` object is available in the document.
kpo_data <- params$kpo_data
type_data <- params$type_data
reason_data <- params$reason_data
respondent_data <- params$respondent_data
time_data <- params$time_data
comms_data <- params$comms_data
info_data <- params$info_data
staff_data <- params$staff_data
responsive_data <- params$responsive_data
fair_data <- params$fair_data
overall_data <- params$overall_data
la <- params$la
year <- params$year
quarter <- params$quarter
named_qrtr <- params$named_qrtr
```

## KPO 4 Score
```{r kpo score text, echo = FALSE, comment = ""}
# Set up text for KPO4 

# Store the number of financial years available for council
Years <- kpo_data %>%
  filter(id == la) %>%
  distinct(`Financial Year`) %>%
  arrange(`Financial Year`) %>%
  mutate("prev_year" = lag(`Financial Year`))
# Filter to selected financial year
dta <- kpo_data %>%
  filter(Quarter == "Year to Date" & `Financial Year` == year)

# Council KPO4
KPO4_ytd <- dta  %>% 
  filter(id == la) %>% 
  pull(KPO_score)
# Scotland KPO4
scotAv_kpo4 <- dta  %>% 
  filter(id == "Scotland") %>% 
  pull(KPO_score)

# Compare council KPO4 values with Scotland and target to create 
# reactive text values
hilow_kpo4 <- if_else(KPO4_ytd > 7.5, 
                      "higher than", 
                      if_else(KPO4_ytd < 7.5, "lower than", "equal to"))
abbel_kpo4 <- if_else(KPO4_ytd > scotAv_kpo4, 
                      "higher than", 
                      if_else(KPO4_ytd < scotAv_kpo4, 
                             "lower than", 
                             "equal to"))

# Store value for previous financial year if there is one
prev_fin_yr <- Years %>%
  filter(`Financial Year` == year) %>%
  pull(prev_year)
KPO4_other <- kpo_data %>%
  filter(Quarter == "Year to Date" & 
           `Financial Year` == prev_fin_yr & 
           id == la) %>%
  pull(KPO_score)

# Create comparison of KPO4 for selected year with other year available
diff_value <- KPO4_ytd - KPO4_other
diff_text <- if_else(diff_value < 0, "lower", "higher")
diff_value <- round(abs(diff_value), 1)
     
# Text for when there is only 1 financial year
text_kpo <- paste0("This indicator summarises performance across all questions, with differential weightings based on importance. For ",
                   la,
                  " in ",
                  year, 
                  " overall performance is at ", 
                  KPO4_ytd, 
                  " for the year to date. This is ",
                  abbel_kpo4,
                  " the Scotland average of ", 
                  scotAv_kpo4,
                  " and ", 
                  hilow_kpo4,
                  " the target value of 7.5.")
     
# Text for when there are more than 1 financial years     
text_multiple_kpo <- paste0("This indicator summarises performance across all questions, with differential weightings based on importance. For ", 
                            la,
                            " in ",
                            year, 
                            " overall performance is at ", 
                            KPO4_ytd, 
                            " for the year to date. This is ", 
                            diff_value,
                            " points ", 
                            diff_text, 
                            " than the performance of ", 
                            KPO4_other, 
                            " in ", 
                            prev_fin_yr, 
                            ". The year to date performance of ", 
                            la, 
                            " in ", 
                            year, 
                            " is ", 
                            abbel_kpo4,
                            " the Scotland average of ", 
                            scotAv_kpo4,
                            " and ", 
                            hilow_kpo4,
                            " the target value of 7.5.")
```

`r ifelse(is.na(prev_fin_yr), text_kpo, text_multiple_kpo)`

```{r echo = FALSE}
# Create graph for KPO4 YTD
     
kpo_ytd_plot_data <- kpo_data %>% 
  filter(Quarter == "Year to Date")
# Set the council values as a factor so the data can be arranged to have the council first regardless of alphabetical order
kpo_ytd_plot_data$id <- factor(kpo_ytd_plot_data$id, 
                               levels = c(la, "Scotland"))
kpo_ytd_plot_data <- arrange(kpo_ytd_plot_data, id)
     
# Store number of years to determine the number of reps for colours of bars
Years <- length(unique(kpo_ytd_plot_data$`Financial Year`))

ggplot(data = kpo_ytd_plot_data,
       aes(x = `Financial Year`, 
           y = KPO_score, 
           fill = id)) +
  geom_bar(stat = "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black") +
  geom_text(aes(label = KPO_score, y = KPO_score + 0.8), 
            vjust = 0,
            position = position_dodge(width = 0.9)) +
  scale_y_continuous(limits = c(0, 11), 
                     expand = expansion(mult = c(0, 0.1))) +
  scale_fill_manual(values = rep(c("cadetblue3", "dimgrey"), Years),
                    name = "") +
  ggtitle("KPO 4 score - Year to Date") +
  xlab("") +
  ylab("KPO 4 Score") +
  theme_classic()
```
\newpage

# Respondent Type
```{r respondent type text, echo = FALSE, comment = ""}
# Set up text for respondent type
type_dta_filter <- respondent_data %>% 
  filter(question_type == "Type") 
# Get total responses for referencing the percentage denominator
type_number <- type_dta_filter %>% 
  group_by(Question) %>%
  summarise("total_responses" = sum(n)) %>%
  distinct(total_responses) %>%
  pull(total_responses)
# Create variables for percentages for different groups
agent_perc <- type_dta_filter %>%
      filter(Question == "Agent/Designer" & value == 1) %>%
      pull(perc)
appli_perc <- type_dta_filter %>%
      filter(Question == "Applicant" & value == 1) %>%
      pull(perc)
contr_perc <- type_dta_filter %>%
      filter(Question == "Contractor" & value == 1) %>%
      pull(perc)
type_other_perc <- type_dta_filter %>%
      filter(Question == "Other respondent" & value == 1) %>%
      pull(perc)

# If any are 0 then replace with "none"
agent_perc <- if_else(is_empty(agent_perc), "none", paste0(agent_perc, "%"))
appli_perc <- if_else(is_empty(appli_perc), "none", paste0(appli_perc, "%"))
contr_perc <- if_else(is_empty(contr_perc), "none", paste0(contr_perc, "%"))
type_other_perc <- if_else(is_empty(type_other_perc), 
                          "No respondents", 
                          paste0(type_other_perc, "%"))
```
  
Respondents were asked to provide details on the type of respondent they were, as well as their reason for contacting the Building Standards Service in `r la`. Of the `r type_number` respondents in `r named_qrtr` `r year`, `r agent_perc` were agents or designers, `r appli_perc` were applicants and `r contr_perc` were contractors. `r type_other_perc` said they were an other respondent type.

```{r respondent type plot, echo = FALSE}
ggplot(data = type_data,
       aes(x = fct_reorder(Question, desc(perc)), 
           y = perc)) +
  geom_col(fill = "cadetblue3", colour = "black") +
  geom_text(aes(label = perc, y = perc + 2.5), 
            vjust = 0,
            position = position_dodge(width = 0.9)) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Respondent Type: \n", named_qrtr, year)) +
  xlab("Respondent Type") +
  ylab("Percentage of Responses")
```
\newpage

# Response Reason
```{r respondent reason text, echo= FALSE, comment = ""}
# Set up text for response reason
resp_dta_filter <- respondent_data %>% 
  filter(question_type == "Reason") 
# Get total responses for referencing the percentage denominator
resp_number <- resp_dta_filter %>% 
  group_by(Question) %>%
  summarise("total_responses" = sum(n)) %>%
  distinct(total_responses) %>%
  pull(total_responses)
# Calculate percentages for each response type
discuss_perc <- resp_dta_filter %>%
  filter(Question == "To discuss your proposal" & value == 1) %>%
  pull(perc)
appli_perc <- resp_dta_filter %>%
  filter(Question == "To make an application" & value == 1) %>%
  pull(perc)
constr_perc <- resp_dta_filter %>%
  filter(Question == "During construction" & value == 1) %>%
  pull(perc)
other_perc <- resp_dta_filter %>%
  filter(Question == "Other reason" & value == 1) %>%
  pull(perc)
     
# If any are 0 then replace with "none"
discuss_perc <- if_else(isEmpty(discuss_perc), 
                        "none", 
                        paste0(discuss_perc,"%"))
appli_perc <- if_else(isEmpty(appli_perc), 
                      "none", 
                      paste0(appli_perc, "%"))
constr_perc <- if_else(isEmpty(constr_perc), 
                       "none", 
                       paste0(constr_perc, "%"))
other_perc <- if_else(isEmpty(other_perc), 
                      "No respondents", 
                      paste0(other_perc, "%"))
```

  
Respondents were asked to provide details on the type of respondent they were, as well as their reason for contacting the Building Standards Service in `r la`. Of the `r resp_number` respondents in, `r named_qrtr` `r year`, `r discuss_perc` contacted the local authority to discuss their proposal before applying for a building warrant, `r appli_perc` were making an application for a warrant and `r constr_perc` contacted the service during construction. `r other_perc` contacted the service for some other reason.  


```{r respondent reason plot, echo = FALSE}
ggplot(data = reason_data,
       aes(x = fct_reorder(Question, desc(perc)), 
               y = perc)) +
  geom_col(fill = "cadetblue3", colour = "black") +
  geom_text(aes(label = perc, y = perc + 2.5), 
            vjust = 0,
            position = position_dodge(width = 0.9)) +
  coord_flip() +
  theme_classic() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste("Respondent Reason: \n", named_qrtr, year)) +
  xlab("Reason") +
  ylab("Percentage of Responses")
```
\newpage

# KPO 4 Over Time
```{r kpo over time text, echo = FALSE, comment = ""}

# Filter data to selected council and quarters only
kpo_over_time_dta <- kpo_data %>%
  filter(Quarter != "Year to Date" & id == la) %>%
  # Add column with quarter & financial years combined
  mutate(Label = str_replace(Quarter, "Quarter ", "Q")) %>%
  mutate(Label = paste(Label, `Financial Year`))

# Set value for current quarter - either quarter selected, or if YTD is
# selected, use most recent quarter in the selected year
current_quarter <- if(named_qrtr == "Year to Date") {
  max_qrtr <- kpo_over_time_dta %>% 
    filter(`Financial Year` == year)
    max(max_qrtr$Quarter)
} else {
  named_qrtr
}
                           
# Store KPO score for currently selected quarter and year
current_value <- kpo_over_time_dta %>%
  filter(Quarter == current_quarter &
           `Financial Year` == year) %>%
  pull(KPO_score)

# Find previous quarter name and value
prev_quarter <- kpo_over_time_dta %>%
  arrange(`Financial Year`) %>%
  mutate("prev_quarter" = lag(Label)) %>%
  filter(Quarter == current_quarter & `Financial Year` == year) %>%
  pull(prev_quarter)

prev_quarter_value <- kpo_over_time_dta %>%
  filter(Label == prev_quarter) %>%
  pull(KPO_score)

# Create comparison of KPO4 for selected quarter with previous quarter available
quarter_diff <- current_value - prev_quarter_value
quarter_diff_text <- if_else(quarter_diff < 0, "lower", "higher")
quarter_diff <- round(abs(quarter_diff), 1)

# Find equivalent quarter in previous year (if available)
prev_year_quarter <- kpo_over_time_dta %>%
  filter(Quarter == current_quarter) %>%
  arrange(`Financial Year`) %>%
  mutate("prev_year_quarter" = lag(Label)) %>%
  filter(`Financial Year` == year) %>%
  pull(prev_year_quarter)

prev_year_quarter_value <- kpo_over_time_dta %>%
  filter(Label == prev_year_quarter) %>%
  pull(KPO_score)

prev_year_quarter <- prev_year_quarter %>%
  str_replace(., "Q[0-9]\\ ", "")

# Create comparison of KPO4 for selected quarter with equivalent quarter
# from previous year (if available)
year_quarter_diff <- current_value - prev_year_quarter_value
year_quarter_diff_text <- if_else(year_quarter_diff < 0, "lower", "higher")
year_quarter_diff <- round(abs(year_quarter_diff), 1)

# Create standard text
main_text <- paste0("In ", 
                    current_quarter, 
                    " ",
                    year, 
                    " performance for KPO4, calculated across all responses for all questions, was ",
                    current_value,
                    " for ",
                    la,
                    ".")

# Create text for previous quarter comparison
prev_quarter_text <- paste0("This is ",
                            quarter_diff,
                            " points ",
                            quarter_diff_text,
                            " than the previous quarter performance of ",
                            prev_quarter_value,
                            " in ",
                            prev_quarter,
                            ".")

# Create text for equivalent quarter in previous year comparison
prev_year_quarter_text <- paste0("KPO4 performance in  ",
                                 current_quarter, 
                                 " ",
                                 year, 
                                 " was ",
                                 year_quarter_diff,
                                 " points ",
                                 year_quarter_diff_text,
                                 " than the performance of ",
                                 prev_year_quarter_value,
                                 " in the same quarter in ",
                                 prev_year_quarter,
                                 ".")

# Conditional statement to select text based on whether there is a previous year to compare   
final_text <- if_else(is.na(prev_quarter) & is.na(prev_year_quarter), 
                      main_text,
                      if_else(!is.na(prev_quarter) & is.na(prev_year_quarter),
                              paste(main_text, prev_quarter_text),
                              paste(main_text, 
                                    prev_quarter_text, 
                                    prev_year_quarter_text)))

```    
    
`r final_text`
    
```{r kpo over time plot, echo = FALSE}
kpo_over_time_plot_dta <- kpo_data %>%
  filter(Quarter != "Year to Date")

# Set the council values as a factor so the data can be arranged to have the # council first regardless of alphabetical order
kpo_over_time_plot_dta$id <- factor(kpo_over_time_plot_dta$id, 
                                    levels = c(la, "Scotland"))
# Add Financial year to quarter labels
kpo_over_time_plot_dta <- kpo_over_time_plot_dta %>%
  mutate(Quarter = str_replace(Quarter, "Quarter ", "Q")) %>%
  mutate(Label = paste(Quarter, `Financial Year`))
# Arrange the data to set the order of colours
kpo_over_time_plot_dta <- kpo_over_time_plot_dta %>%
  arrange(`Financial Year`, Quarter, id)
# Set the date labels as a factor to ensure they stay in order
kpo_over_time_plot_dta$Label <- factor(kpo_over_time_plot_dta$Label,
                                       levels = unique(kpo_over_time_plot_dta$Label))

ggplot(data = kpo_over_time_plot_dta,
       aes(x = Label,
           y = KPO_score, 
           group = id, 
           colour = id)) +
  geom_line(lwd = 1) +
  geom_text(aes(label = KPO_score, 
                y = KPO_score + 0.1), 
            vjust = 0,
            position = position_dodge(width = 0),
            show.legend = FALSE) +
  scale_color_manual(values = c("cadetblue3", "dimgrey"), 
                     name = "") +
  ggtitle("KPO 4 score - over time") +
  ylim(0, 10.5) +
  xlab("") +
  ylab("KPO 4 Score") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1))
```
  
```{r text function, echo = FALSE, comment = ""}
# Create function for preparing text values for individual questions
text_prep <- function(dataset, 
                      question, 
                      named_value_1, 
                      named_value_2,
                      extra_text) {
  # Load data and split into Scotland and LA datasets
  qstnDta_LA <- dataset %>% 
    filter(Selection == la)
  qstnDta_scot <- dataset %>% 
    filter(Selection == "Scotland")
  # Get total percentage positive
  total_good <- qstnDta_LA  %>%
      filter(value %in% c(1,2)) %>% 
      pull(perc_resp) %>%
      sum()
  # If this is above 55% then overall is positive, If less than 45%
  # negative, otherwise balanced
  pos_or_neg <- if_else(total_good > 55, 
                        "mainly positive", 
                        if_else(total_good < 45, 
                               "mainly negative", 
                               "balanced"))
  # Add "only" to the % positive if this is below 45
  if (total_good < 45) {
    total_good <- paste("only", total_good)
  } else {
    total_good <- total_good
    }
  
  # Get the name for the maximum value in LA dataset. If more than one 
  # paste these together
  max_name <- qstnDta_LA %>% 
    filter(perc_resp == max(perc_resp)) %>% 
    pull(named_value)
  # Get the percentage for the highest response and paste together if multiple
  max_perc <- qstnDta_LA %>% 
    filter(named_value %in% max_name) %>% 
    distinct(perc_resp) %>%
    pull(perc_resp)
  if (length(max_name) > 1) {
    max_perc <- paste(max_perc, "percent respectively.")
  } else {
    max_perc <- paste0(max_perc, " percent.")
  }
  if (length(max_name > 1)) {
    max_name <- paste(max_name, collapse = " & ")
  }
  # Get second highest value
  sec_val <- sort(unique(qstnDta_LA$perc_resp), 
                  decreasing = TRUE) %>%
    nth(2)
  # Filter for second highest value's name
  sec_name <- qstnDta_LA %>%
    filter(perc_resp == sec_val) %>% 
    pull(named_value)
  # Create text, accounting for more than one same value
  if (length(sec_name) > 1) {
    sec_perc <- paste(sec_val, "percent respectively.")
  } else {
    sec_perc <- paste0(sec_val, " percent.")
  }
  if (length(sec_name) > 1) {
    sec_name <- paste(sec_name, collapse = " & ")
  }
  # Get most frequent response for Scotland
  scot_max_name <- qstnDta_scot %>% 
    filter(perc_resp == max(perc_resp)) %>% 
    pull(named_value)
  if (length(scot_max_name) > 1) {
    scot_max_name <- paste(scot_max_name, collapse = " & ")
  }
  # Get percentage for most frequent Scotland level response
  scot_max_perc <- qstnDta_scot %>% 
    filter(perc_resp == max(perc_resp)) %>% 
    distinct(perc_resp) %>%
    pull(perc_resp)
  if (length(scot_max_name) > 1) {
    scot_max_perc <- paste(scot_max_perc, "percent respectively.")
  } else {  
    scot_max_perc <- paste0(scot_max_perc, " percent.")
  }
  
   # Paste the text together
  main_text <- paste0("In ",
                      quarter,
                      " ",
                      year,
                      ", in relation to the statement \"",
                      question,
                      "\" responses for ",
                      la,
                      " have been ",
                      pos_or_neg, 
                      " with ",
                      total_good,
                      " percent saying that ",
                      extra_text,
                      " ",
                      named_value_1,
                      " or ",
                      named_value_2,
                      ". The greatest proportion of respondents said ",
                      extra_text,
                      " ",
                      max_name,
                      " at ", 
                      max_perc, 
                      " This was followed by ", 
                      sec_name, 
                      " at ", 
                      sec_perc,
                      " For Scotland overall, most respondents said that ",
                      extra_text,
                      " ",
                      scot_max_name,
                      " at ", 
                      scot_max_perc)
  
  # Text when all responses are the same
  other_text <- paste0("In ",
                       quarter,
                       " ",
                       year,
                       ", in relation to the statement \"",
                       question,
                       "\" responses for ",
                       la,
                       " have been ",
                       pos_or_neg, 
                       " with ",
                       total_good,
                       " percent saying that ",
                       extra_text,
                       " ",
                       named_value_1,
                       " or ",
                       named_value_2,
                       ". The greatest proportion of respondents said ",
                       extra_text,
                       " ",
                       max_name,
                       " at ", 
                       max_perc, 
                       " For Scotland overall, most respondents said that ",
                       extra_text,
                       " ",
                       scot_max_name,
                       " at ", 
                       scot_max_perc)
  
  # Test whether there's more than one different type of response
    text <- ifelse(is.na(sec_val), other_text, main_text)
}
```

```{r plot function, echo = FALSE}
plot_prep <- function(data, title) {
  ggplot(data = data,
         aes(x = fct_reorder(named_value, value), 
             y = perc_resp, 
             fill = Selection)) +
  geom_bar(stat = "identity", 
           position = "dodge",
           width = 0.7,
           colour = "black") +
  geom_text(aes(label = perc_resp, y = perc_resp + 1.2), 
            vjust = 0,
            position = position_dodge(width = 0.9)) +
  scale_fill_manual(values = c("cadetblue3", 
                               "dimgrey"), 
                    name = "") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  ggtitle(paste(title, 
                named_qrtr, 
                year)) +
  xlab("Responses") +
  ylab(paste("% of Responses", named_qrtr, year)) +
  theme_classic()
}
```

\newpage

# Individual Questions

## Time taken

```{r time taken text, echo = FALSE}
time_taken_text <- text_prep(dataset = time_data,
                             question = "How satisfied were you with the time taken?",
                             named_value_1 = "very satisfied",
                             named_value_2 = "satisfied",
                             extra_text = "they were")
```
`r time_taken_text` 

```{r time taken plot, echo = FALSE}
plot_prep(data = time_data, 
          title = "Satisfaction with time taken -")
```

\newpage

## Communications
```{r comms text, echo = FALSE, comment = ""}
comms_text <- text_prep(dataset = comms_data,
                             question = "How would you rate the standard of communication?",
                             named_value_1 = "very good",
                             named_value_2 = "good",
                             extra_text = "it was")
```
`r comms_text`

```{r comms plot, echo = FALSE}
plot_prep(data = comms_data, title = "Standard of communication -")
```

\newpage

## Information
```{r info text, echo = FALSE, comment = ""}
info_text <- text_prep(dataset = info_data,
                       question = "Quality of the information provided",
                       named_value_1 = "very good",
                       named_value_2 = "good",
                       extra_text = "it was")
```
`r info_text`

```{r info plot, echo = FALSE}
plot_prep(data = info_data, title = "Quality of information -")
```

\newpage

## Staff
```{r staff text, echo = FALSE, comment = ""}
staff_text <- text_prep(dataset = staff_data,
                        question = "Service offered by staff",
                        named_value_1 = "very good",
                        named_value_2 = "good",
                        extra_text = "it was")
```
`r staff_text` 

```{r staff plot, echo = FALSE}
plot_prep(data = staff_data, title = "Service offered by staff -")
```

\newpage

## Responsiveness
```{r responsiveness text, echo = FALSE, comment = ""}
responsive_text <- text_prep(dataset = responsive_data,
                             question = "Responsiveness to any queries or issues raised",
                             named_value_1 = "very good",
                             named_value_2 = "good",
                             extra_text = "it was")
```
`r responsive_text`

```{r responsiveness plot, echo = FALSE}
plot_prep(data = responsive_data,
          title = "Responsiveness to queries or issues -")
```

\newpage

## Treated Fairly
```{r treated fairly text, echo = FALSE, comment = ""}
fairly_text <- text_prep(dataset = fair_data,
                         question = "To what extent would you agree that you were treated fairly?",
                         named_value_1 = "strongly agree",
                         named_value_2 = "agree",
                         extra_text = "they")
```
`r fairly_text` 

```{r treated fairly plot, echo = FALSE}
plot_prep(data = fair_data,
          title = "Would you agree you were treated fairly -")
```

\newpage

## Overall Satisfaction
```{r overall satisfaction text, echo = FALSE, comment = ""}
overall_text <- text_prep(dataset = overall_data,
                          question = "How satisfied were you overall?",
                          named_value_1 = "very satisfied",
                          named_value_2 = "satisfied",
                          extra_text = "they were")
```
`r overall_text`  

```{r overall satisfaction plot, echo = FALSE}
plot_prep(data = overall_data, title = "Overall satisfaction -")
```